Temporal Variations In Vapor Intrusion-Induced Indoor Air Contaminant Concentrations

### 2019-04-01 tex/main.tex
More edits

% authors
\author{Jonathan G. V. Ström}
\affiliation[Brown University]{Brown University, School of Engineering, Providence, RI, USA}
\author{Yijun Yao}
\affiliation[Brown University]{Brown University, School of Engineering, Providence, RI, USA}
\author{Yuanming Guo}
\affiliation[Arizona State University]{Arizona State University}
\author{Eric M. Suuberg}
\email{eric_suuberg@brown.edu}
\affiliation[Brown University]{Brown University, School of Engineering, Providence, RI, USA}

@@

  Unsteady-CSTR                            & $V\frac{d u}{d t} = \int_{A_\mathrm{ck}} j_\mathrm{ck} dA - u A_e V$                                                                  \\

@@

  At foundation crack          & $p = p_\mathrm{in/out} \; \mathrm{(Pa)}$ & $j_\mathrm{ck} = \frac{u c}{1 - \exp{(u L_\mathrm{slab}/D_\mathrm{air})}}$ \\

@@

  At groundwater source        & N/A                                      & $c = c_\mathrm{gw} K_H \; \mathrm{(\mu g/m^3)}$                            \\

@@

  At ground surface            & $p = 0 \; \mathrm{(Pa)}$                 & $c = 0 \; \mathrm{(\mu g/m^3)}$                                            \\

@@

  Exit of preferential pathway & $p = 0 \; \mathrm{(Pa)}$                 & $c = c_\mathrm{gw} K_H \chi \; \mathrm{(\mu g/m^3)}$                       \\

@@

  Soil       & $\text{Permeability} \; \mathrm{(m^2)}$ & $\mathrm{Density} \; \mathrm{(kg/m^3)}$ & $\theta_s$ & $\theta_r$ & $\alpha \; \mathrm{(1/m)}$ & $n$ \\

@@

  $D_\mathrm{air} \; \mathrm{(m^2/h)}$ & $D_\mathrm{water} \; \mathrm{(m^2/h)}$ & $\mathrm{Density} \; \mathrm{(kg/m^3)}$ & $\mathrm{Viscosity} \; \mathrm{(Pa \cdot s)}$ & $K_H$ & $M \; \mathrm{(g/mol)}$ \\

@@

>>>>

% authors
\author{Jonathan G. V. Ström}
\affiliation[Brown University]{Brown University, School of Engineering, Providence, RI, USA}
\author{Yijun Yao}
\affiliation[Brown University]{Brown University, School of Engineering, Providence, RI, USA}
%\author{Yuanming Guo}
%\affiliation[Arizona State University]{Arizona State University}
\author{Eric M. Suuberg}
\email{eric_suuberg@brown.edu}
\affiliation[Brown University]{Brown University, School of Engineering, Providence, RI, USA}

@@

  Unsteady-CST                            & $V\frac{d c_\mathrm{in}}{d t} = \int_{A_\mathrm{ck}} j_\mathrm{ck} dA - c_\mathrm{in} A_e V_\mathrm{slab}$                                                                  \\

@@

  Foundation crack          & $p = p_\mathrm{in/out} \; \mathrm{(Pa)}$ & $j_\mathrm{ck} = \frac{u c}{1 - \exp{(u L_\mathrm{slab}/D_\mathrm{air})}}$ \\

@@

  Groundwater source        & \textit{No flow}                                      & $c = c_\mathrm{gw} K_H \; \mathrm{(\mu g/m^3)}$                            \\

@@

  Groundsurface            & $p = 0 \; \mathrm{(Pa)}$                 & $c = 0 \; \mathrm{(\mu g/m^3)}$                                            \\

@@

  Preferential pathway & $p = 0 \; \mathrm{(Pa)}$                 & $c = c_\mathrm{gw} K_H \chi \; \mathrm{(\mu g/m^3)}$                       \\

@@

  Soil       & $\kappa_s \; \mathrm{(m^2)}$ & $\rho \; \mathrm{(kg/m^3)}$ & $\theta_s$ & $\theta_r$ & $\alpha \; \mathrm{(1/m)}$ & $n$ \\

@@

  $D_\mathrm{air} \; \mathrm{(m^2/h)}$ & $D_\mathrm{water} \; \mathrm{(m^2/h)}$ & $\rho \; \mathrm{(kg/m^3)}$ & $\mu \; \mathrm{(Pa \cdot s)}$ & $K_H$ & $M \; \mathrm{(g/mol)}$ \\

@@

\begin{table}[htb!]
  \caption{List of abbreviations}\label{tbl:abbreviations}
\begin{tabular}{l l}
  \toprule
  % A/ALPHA
  $A_\mathrm{ck}$ & Crack area \\
  $A_e$ & Air exchange rate \\
  $\alpha, \; n, \; m, \; l$ & van Genuchten parameters \\
  $\alpha_\mathrm{gw}$ & Attenuation from groundwater contaminant vapor source \\
  % C
  $c_\mathrm{in}$ & Indoor air contaminant concentration \\
  $c$ & Soil-gas contaminant concentration \\
  $c_w$ & Soil-water contaminant concentration \\
  $c_\mathrm{gw}$ & Contaminant groundwater concentration \\
  $\chi$ & Preferential pathway contaminant concentration scaling parameter \\
  % D
  $D_\mathrm{eff}$ & Effective diffusion coefficient \\
  $D_\mathrm{air}$ & Diffusion coefficient in air \\
  $D_\mathrm{water}$ & Diffusion coefficient in water \\
  % J
  $j_\mathrm{ck}$ & Contaminant molar flux through the foundation crack \\
  % K
  $\kappa_s$ & Saturated soil permeability \\
  $K_H$ & Dimensionless Henry's law constant \\
  $k_r$ & Relative permeability \\
  % L
  $L_\mathrm{slab}$ & Thickness of the foundation slab \\
  % M
  $M$ & Molar mass \\
  $\mu$ & Contaminant vapor viscosity \\
  % N
  NAS & Naval Air Stations \\
  % P
  $p$ & Pressure in soil \\
  $p_\mathrm{in/out}$ & Indoor/outdoor pressure difference \\
  PP & Preferential pathway \\
  % R
  $\rho$ & Density \\
  % S
  $\mathrm{Se}$ & Soil water saturation \\
  % T
  $t$ & time \\
  $\theta_g$ & Vapor/gas filled porosity \\
  $\theta_w$ & Water filled porosity \\
  $\theta_r$ & Residual water filled porosity \\
  $\theta_t$ & Total porosity \\
  % U
  $\vec{u}$ & Soil-gas velocity (vector quantity) \\
  % V
  VI & Vapor intrusion \\
  $V_\mathrm{base}$ & Basement volume \\
  % Z
  $z$ & Elevation above groundwater \\
  \bottomrule
\end{tabular}
\end{table}
